---
title: "final_code"
output: pdf_document
date: "2025-07-12"
---

# Setup Libraries
```{r setup, include=FALSE}
library(haven)
library(dplyr)
library(tidyr)
library(ggplot2)
library(estimatr)
library(stargazer)
library(ggplot2)
library(data.table)
library(xtable)
library(bacondecomp)
```

# Analyzing Civil War Incidents 
```{r}
## load the incidents data 
incidents_df <- read.csv("incidents_cleaned.csv")

plot <- ggplot(incidents_df, aes(x=as.factor(year), fill=incident_description)) +     
        geom_bar() + 
        theme(axis.text.x = element_text(angle = 90, size = 10)) + 
        labs(y="Victim Count", x="Year") +
        guides(fill=guide_legend(title="Incident Type"))
print(plot)
ggsave("incident_barplot.pdf", plot, width=11, height=6)
```

# Difference-in-Difference Analysis 

## Load data
```{r}
## load the full raw_data 
full_data <- read_dta("clean_parliament_data.dta")
main_sub <- full_data[c("District", "year", "turnout_vage", "high_conflict_gov")]

## load the data cleaned for DiD Analysis
did_data <- read.csv("did_data.csv")
did_data$post <- as.integer(did_data$year >= did_data$treat_year)
did_data$treat_year <- ifelse(did_data$treat_year != 2010, did_data$treat_year, 2025)
did_data$interaction <- did_data$post * did_data$treated
did_data$high_conflict_casualty <- full_data$high_conflict_gov
```

## Plot of Victim Counts for High and Low Conflict Districts
```{r}
subset_2008 <- subset(full_data, year==2008)
subset_2008$conflict_intensity <- "High"
subset_2008$conflict_intensity[subset_2008$high_conflict_pop == 0] <- "Low"
plot <- ggplot(data=subset_2008, aes(x=as.factor(District), y=vic_cn, 
                                     fill=factor(conflict_intensity))) + 
        geom_bar(stat="identity") +
        theme_bw() + 
        labs(y="Victim Count", x="District", title="Victim Counts by Districts")+
        theme(axis.text.x = element_text(angle = 90, size = 7.5))+
        guides(fill=guide_legend(title="Conflict Intensity")) +
        theme(plot.title = element_text(hjust = 0.5)) 
print(plot)

ggsave("conflict_barplot_distict_pop.pdf", plot, width=11, height=6)
```

## Visual Test for Parallel Trends
```{r}
data_voter <- did_data[c("District", "year", "turnout_vage", "high_conflict_gov")]
high_district <- unique(data_voter$District[data_voter$high_conflict_gov==1])
data_voter$all_high <- as.numeric(data_voter$District  %in% high_district)
test_agg_high <- aggregate(turnout_vage~year+all_high, data=data_voter, 
                           mean, na.action = NULL, na.rm=FALSE)
test_agg_high$intensity <- "high"
test_agg_high$intensity[test_agg_high$all_high == 0] <- "low"
test_agg_high$turnout_rate <- test_agg_high$turnout_vage / 100

line_plot <- ggplot(data=test_agg_high, aes(x=year, y=turnout_rate, group=intensity)) +
  geom_line(aes(color=intensity)) +
  geom_point() +
  labs(y="Turnout Rate", x="Year", title="Voter Turnout Rates") +
  guides(color = guide_legend(title = "Conflict Intensity")) +
  scale_x_continuous(breaks = seq(1990, 2014, by = 2)) +
  theme(plot.title = element_text(hjust = 0.5)) 
print(line_plot)
ggsave("parallel_trend_.pdf",line_plot, width=7, height=2.5)
```
## Two Way Fixed Effects (TWFE)
$$Y_{i, t} = \omega + \delta D_{i, t} + \alpha_i +  \gamma_t + \epsilon_{i, t}$$
where $Y_{it}$: voter turnout rate at time t, $D_{it}$: dummy variable represent conflict intensity in district i at time t (1 = high intensity conflict), $\alpha$: district fixed effects, $\gamma$: time fixed effects, $\epsilon_{i, t}$: error term

```{r}
model1 <- lm(turnout_rate ~ interaction + factor(year) + factor(District), data=did_data) 
summary(model1)
```

## TWFE with Covariates 
$$Y_{i, t} = \omega + \delta D_{i, t} + \beta X_{i, t} + \alpha_i +  \gamma_t + \epsilon_{i, t}$$
 where $X_{i, t}$ denotes the literacy rate of district i at time t; all other variables are defined as in the TWFE specification. 
```{r}
## load the literacy rate data 
literacy_data <- read.csv("literacy_pooled_data.csv", check.names = FALSE)
did_data_covar <- merge(did_data, literacy_data, by=c("year", "District"))
did_data_covar$literacy_rate <- did_data_covar$literacy_rate / 100
model1 <- lm(turnout_rate ~ interaction + literacy_rate + factor(year) + factor(District), 
             data=did_data_covar) 
summary(model1)
```

## Callaway and Sant'Anna model 
```{r}
did_data$district_id <- as.numeric(factor(did_data$District))
results <- att_gt(yname = "turnout_rate", tname="year", idname="district_id", 
                  gname="treat_year", data=did_data)
agg_result <- aggte(results, type = "dynamic", min_e = -15, max_e = 15)

fig <- ggdid(agg_result)
fig <- fig + labs(x = "time (years)", y = "ATT-estimate")
ggsave(filename = "ggdid_plot.pdf", plot = fig, 
       width = 6, height = 4, dpi = 300)
print(fig)
```

### Summarize Staggered DiD Result
```{r}
agg_result
```


## Goodman-Bacon decomposition 
```{r}

data_bacon <- did_data %>% filter(!is.na(turnout_rate))
names(data_bacon)[names(data_bacon) == "treated"] <- "high_conflict"
district_year_counts <- data_bacon %>%
  group_by(district_id) %>%
  summarise(n_years = n_distinct(year))

complete_districts <- district_year_counts %>%
  filter(n_years == length(unique(data_bacon$year))) %>%
  pull(district_id)

data_bacon_balanced <- data_bacon %>%
  filter(district_id %in% complete_districts)
bgd <- bacon(turnout_rate ~ interaction,
             data = data_bacon_balanced %>% mutate(treat_year = ifelse(treat_year==2025, NA, treat_year)),
             id_var = "district_id",
             time_var = "year"
             )
bgd_wm = weighted.mean(bgd$estimate, bgd$weight)

ggplot(bgd, aes(x = weight, y = estimate, shape = type, col = type)) +
  geom_hline(yintercept = bgd_wm, lty  = 2) +
  geom_point(size = 3) +
  labs(x = "Weight", y = "Estimate", shape = "Type", col = "Type",
       title = "Bacon-Goodman decomposition example",
       caption = "Note: Horizontal dotted line represents the full TWFE estimate.") +
       theme(plot.title = element_text(hjust = 0.5)) 
```
